Shallow EDSLs and Object-Oriented Programming

### 2016-06-28 paper/paper.tex
local
One pass
Address comments
Conclusion
More changes
Author

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\authorinfo{}
           {}
           {}
%\authorinfo{Name}
%           {Affiliation2/3}
%           {Email2/3}

@@

%===============================================================================
\input{sections/Introduction.tex}
\input{sections/ShallowOO.tex}
\input{sections/Transformations.tex}
\input{sections/Modularity.tex}
\input{sections/RelatedWorkShort.tex}
%\input{sections/Overview.tex}
%\input{sections/Tool.tex}
%\input{sections/CaseStudy.tex}
%\input{sections/RelatedWork.tex}
%\input{sections/Discussion.tex}
%\acks

>>>>

\setlist[itemize]{noitemsep,nolistsep}
\setlist[enumerate]{noitemsep,nolistsep}

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{Shallow EDSLs and Object-Oriented Programming}   % 'preprint' option specified.

@@

\authorinfo{Weixin Zhang \and Bruno C.d.S.Oliveira}
           {The University of Hong Kong, Pokfulam, Hong Kong, China}
           {\{wxzhang2,bruno\}@cs.hku.hk}
%\authorinfo{Name}
%           {Affiliation2/3}
%           {Email2/3}

@@

%===============================================================================
\input{sections/Introduction.tex}
\input{sections/ShallowOO.tex}
\input{sections/Interpretations.tex}
\input{sections/Transformations.tex}
%\input{sections/RelatedWorkShort.tex}
\input{sections/Conclusion.tex}
%\input{sections/Modularity.tex}
%\input{sections/Overview.tex}
%\input{sections/Tool.tex}
%\input{sections/CaseStudy.tex}
%\input{sections/RelatedWork.tex}
%\input{sections/Discussion.tex}
%\acks
